Embodied Neuromorphic Benchmarks

### 2015-08-26 paper/paper.tex
Fixed typos

Given the success of this approach for evolutionary robotics, we propose
using minimal simulation for neuromorphic benchmarks.  We would argue that
one important use of a benchmark is \emph{generalization}.  That is, by knowing how well particular
hardware performs on a benchmark, you can reasonably infer how well
that hardware will perform in other situations.  For example, if an image recognition
algorithm performs well on the MNIST hand-written digit recognition
benchmark, this suggests that it may also perform well on
a different recognition task.  Of course, this inference will fail if that
algorithm has been specifically over-fit to that situation.  For
that reason, it is useful to have benchmarks that covers a wide range
of variations on the task.  If the hardware performs well across that
variability, then it is more likely to also work in sufficiently similar new situations.

@@

To run a benchmark using the proposed
minimal simulation approach, there are three main steps: 1. identify
the neuromorphic hardware to be tested; 2. construct the minimal
simulation; 3. determine a metric (e.g. root-mean-squared error; rmse)
to record; 5. specify distributions for any parameters in the
simulation.  We then perform multiple runs of the simulation, each
time choosing different values from the parameter distributions.  We
can then plot how the metric varies as a function of a particular parameter
of interest, or how it compares across different hardware for a
given set of parameter distributions.

>>>>

Given the success of this approach for evolutionary robotics, we propose
using minimal simulation for neuromorphic benchmarks.  We would argue that
one important use of a benchmark is \emph{generalization}.  That is, by knowing how well particular
hardware performs on a benchmark, you can reasonably infer how well
that hardware will perform in other situations.  For example, if an image recognition
algorithm performs well on the MNIST hand-written digit recognition
benchmark, this suggests that it may also perform well on
a different recognition task.  Of course, this inference will fail if that
algorithm has been specifically over-fit to that situation.  For
that reason, it is useful to have benchmarks that cover a wide range
of variations on the task.  If the hardware performs well across that
variability, then it is more likely to also work in sufficiently similar new situations.

@@

To run a benchmark using the proposed
minimal simulation approach, there are four main steps: 1. identify
the neuromorphic hardware to be tested; 2. construct the minimal
simulation; 3. determine a metric (e.g. root-mean-squared error; rmse)
to record; 4. specify distributions for any parameters in the
simulation.  We then perform multiple runs of the simulation, each
time choosing different values from the parameter distributions.  We
can then plot how the metric varies as a function of a particular parameter
of interest, or how it compares across different hardware for a
given set of parameter distributions.
